Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
Image adjustment
.

::: {.cell}
![Predicted Electoral Votes for the 2024 US Election ](../other/images/Election_map.png){fig-align="center" width="50%"}
:::

## Limitations and Weaknesses
- nuemric_grade couldve been used to weigh pollster results, for accuracy 
- lack of real time adjustments 
- less data to use becuase we are only considering data since Harris's declaration as a candidate 
- limited scope of variables (demographic changes, economic conditions, and recent events, are not included)
- some ambiguity of results, nothing to compare to

>>>>

::: {.cell}
![Predicted Electoral Votes for the 2024 US Election ](../other/images/Election_map.png){fig-align="center" width="100%"}
:::

## Limitations and Weaknesses

There are several limitations and weaknesses thatcould have affected out research and statistical analysis. First, the variable ****
- nuemric_grade couldve been used to weigh pollster results, for accuracy 
- lack of real time adjustments 
- less data to use becuase we are only considering data since Harris's declaration as a candidate 
- limited scope of variables (demographic changes, economic conditions, and recent events, are not included)
- some ambiguity of results, nothing to compare to
